%-------------------------
% Resume in Latex
% Author : David Hunter 
% License : MIT
%------------------------

\documentclass[letterpaper,10pt, sans]{article}

% ----- Select the appropriate packages below ----- 
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage[usenames,dvipsnames]{color}
\usepackage{enumitem}                       % This package provides user control over the layout of the three basic list environments: enumerate, itemize and description.
\usepackage[english]{babel}                 % Change this if you want to support a different language
\usepackage{tabulary}                       % 
\usepackage{tabularx}                       % Extends the tabular to add a column to fill out the whitespace b/t two columns
\usepackage{fancyhdr}                       % For headers and footer custimization
\usepackage{lastpage}                       % Allows referring to pages in the document.  Used for x of lastpage.

% Uncomment if you need any of these optional packages.
\usepackage[hidelinks]{hyperref}          % Use if you want to have hyperlinks.
\usepackage[T1]{fontenc}
%\usepackage{latexsym}                    % Use if you need access to lasy fonts
%\usepackage{marvosym}                    % Use if you need European currency symbols.
%\usepackage{verbatim}                    % Allows printing exactly what is typed.

\input{glyphtounicode}                    % Make sure the output is parsable by resume Automatic Tracking Systems

% ----- Setup the page style options below ----- 
\fancyhf{}                                % clear all header and footer fields
%\fancyfoot[L]{\thepage\ of \pageref{LastPage}}
\setlength{\footskip}{13.59999pt}

\pagestyle{fancy}
\thispagestyle{empty}                     % THis will cause the first page not to be numbered

\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-0.5in}
\addtolength{\textheight}{1.0in}


\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
    \vspace{-4pt}
    \scshape
    \raggedright
    \large
  }{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1                      % Ensure that generate pdf is machine readable/ATS parsable

% ----- Custom commands -----

% ----- Company and a single position. -----
\newcommand{\resumeCompanyHeading}[4]{
  \vspace{-1pt}
    \item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{#2} \\
      \textbf{#3} & \textbf{#4}
    \end{tabular*}\vspace{-1pt}
  }

% ----- Multiple Positions Heading in the same company -----
\newcommand{\resumeCompanyPositionHeading}[2]{
    \vspace{-1pt}
      \item
      \begin{tabular*}{1.0\textwidth}{l@{\extracolsep{\fill}}r}
        \textbf{#1} & \textbf{#2}
    \end{tabular*}\vspace{-1pt}
}

% ----- Puts a job description under a Company -----
\newcommand{\resumeJobDescription}[1][]{
    \vspace{-1pt}\par{#1}
}

% ----- Listing for college or courses -----
\newcommand{\resumeEducationHeading}[3]{
  \item 
    \vspace{-1pt}
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{#2} \\
      {#3}
    \end{tabular*}
    \vspace{-20pt}
  }

  % ----- Used for volunteer or other type of activities -----
  \newcommand{\resumeVolunteerHeading}[2]{
    \item 
      \vspace{-1pt}
      \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
        {#1} & #2
      \end{tabular*}
      \vspace{-29pt}
    }

% ----- Patents & Papers -----
  \newcommand{\resumePatentsHeading}[2]{
    \item 
      \vspace{-1pt}
      \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
        \textbf{#1, } & #2
      \end{tabular*}
      \vspace{-29pt}
    }

\newcommand{\resumeItem}[2]{\item{{\textbf{#1}}: {#2 \vspace{1pt}}}}
\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeHeadingListStart}{\begin{description}[leftmargin=0cm]}
\newcommand{\resumeHeadingListEnd}{\end{description}}

\newcommand{\resumeItemListStart}{\begin{itemize}}\vspace{-1pt}
\newcommand{\resumeItemListEnd}{\end{itemize}}\vspace{-1pt}

% ------------------------------
%-----  Start resume here  -----
% ------------------------------
\begin{document}

%----- Header -----
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
    \textbf{David Hunter} & Email : \href{mailto:dph@alumni.neu.edu}{dph@alumni.neu.edu}\\
    \href{https://linkedin.com/in/hunterdp}{https://linkedin.com/in/hunterdp} & Mobile : +1-650-814-1346
\end{tabular*}

%----- Expereince -----
\section{\textbf{Experience}}
    \resumeHeadingListStart
        \resumeCompanyHeading
          {Hewlett Packard Enterprise}
          {San Jose, CA}
          {Vice President Engineering \& Chief Strategist, Hewlett Packard Labs}
          {Mar 2015 - present}
            \resumeItemListStart
                \resumeItem{Management}{Team of program managers and strategist to support research programs \& projects.}
                \resumeItem{Play to Win Strategies}{Disruptive Development Process, Aura Zero Trust Framework, High Performance Computing \& Trustworthy AI strategies.}
                \resumeItem{Governance Process}{Stage-gate model to manage  disruptive research projects \& existing programs.}
                \resumeItem{Information Repository}{Automated and self-service BI based system for tracking programs \& projects.}
                \resumeItem{Advisory Board}{Created an executive level committee of business \& technical experts to provide advice \& insights on internal research activities.}
                \resumeItem{Investments \& Acquisitions}{Drove the acquisition of Simplivity, Quattro Networks and Plexxi.  Created the partnership and investment in Platform9.}
                \resumeItem{Workloads as a Service}{Architecture that provided the ability for application workload execution brokering to the appropriate execution domain, across 
                           physical hosts, virtual machines or containers.}
                \resumeItem{HyperConverged}{Devised multiple architecture strategies to enter the HCI market, finalized by the acquisition of Simplivity.}
                \resumeItem{Technical Career Path}{Chaired two division technical promotion boards and a member of corporate Fellow/Senior Fellow promotion board.}
            \resumeItemListEnd

        \resumeCompanyHeading
            {VMware}
            {Palo Alto, CA}
            {Chief Architect, Software Defined Data Center Business Unit}
            {Jan 2012 - Mar 2015}
            \resumeItemListStart
                \resumeItem{Management}{30 person Platform Security Engineering \& 500 person Global Quality Engineering teams.}
                \resumeItem{Business Development}{Application of virtualization in the automotive, IoT, industrial \& entertainment markets.}
                \resumeItem{Secure Thin Hypervisor}{Bare metal hypervisor for Cloud Native Application development \& server management.}
                \resumeItem{Security Response Center}{Tools \& processes to reduce likelihood of vulnerabilities \& their impact to customers.}
                \resumeItem{CVSS for Virtualization}{Revised scoring system that better categorized vulnerabilities.}
                \resumeItem{Security Score Cards}{Engineering wide, consistent model to measure individual products against a common set of security objectives.}
                \resumeItem{Security Education/Training}{World-wide engineering formal \& informal training programs for 5,000 engineers.}
                \resumeItem{Capital Savings}{Company wide infrastructure inventory and reservation system that eliminated \$5M/year capital expense.}
                \resumeItem{Predictive Analytics}{Tools that improved testing estimations, eliminated duplicative \& identified testing gaps.}
                \resumeItem{CQE Alignment}{Realigned System \& Functional QA to development teams that improved production, increase collaboration \& decrease duplication.}
            \resumeItemListEnd
  
          \resumeCompanyPositionHeading
            {Chief Technology Officer for Worldwide Public Sector, Office of the CTO}
            {Sep 2008 - Dec 2011}
            \resumeItemListStart
                \resumeItem{Business Growth}{Evangelism contributed to growing the US Federal business from \$50M to \$500M.}
                \resumeItem{Cloud Computing}{Member of National Institute of Standards effort to develop SP-500 series.}
                \resumeItem{IPv6}{Drove the prioritized implementation of IPv6 in products to meet US Federal requirements.}
                \resumeItem{High Assurance Platform}{Moved the multi-level security domain system product from a customized hypervisor to a 
                  commercial version of VMware Workstation, including federal security assurance requirements.}
                \resumeItem{Secure Hypervisor}{Led the development of a prototype of a highly secure bare metal client hypervisor. Client platform leveraged
                  functionalities, scalability and stability of ESX while preserving device compatibility of a legacy desktop system.}
            \resumeItemListEnd
  
          \resumeCompanyPositionHeading 
          {Director of Engineering, Ecosystems Engineering}
          {Nov 2004 - Sep 2008}
            \resumeItemListStart
                \resumeItem{Management}{70 person world-wide engineering organization working with OEMs, IHVs \& ISVs.}
                \resumeItem{Hardware Compatibility List}{Transitioned from static documents to a public facing database driven website}
                \resumeItem{OEM Preferred Operating System}{New versions of vSphere supported at release by all major system OEMs.}
                \resumeItem{Certification Suite}{An automated testing suite that increased the number of supported servers and storage arrays
                             from 20 \& 5 to over 2000 \& 200 devices in 2 years.}
                \resumeItem{Security Certifications}{Achieved Common Criteria EAL 4 and FIP-140-2 cryptographic certifications.}
            \resumeItemListEnd
  
          \resumeCompanyHeading
            {SQU Systems}{Palo Alto, CA}
            {Software Consultant}{Sep 2001 - Nov 2002}
              \resumeJobDescription{
                Early stage startup working on “Software Hot Swapping” technology to patch and replace sections of a running operating
                systems.  Effort was moved off-shore and shutdown.}

          \resumeCompanyHeading
            {Compaq Computer Corporation}{Palo Alto, CA}
            {Director Software Engineering, Advanced Technologies Group}{Jan 1998 - Sep 2001}
            \resumeItemListStart
                \resumeItem{Management}{20-person, multi-location engineering organization within the corporate research organization}
                \resumeItem{Digital Continuous Profiling Infrastructure}{Developed image manipulation library for Windows NT, both Intel and Alpha architectures.}
                \resumeItem{Dynamic Optimizer}{A prototype dynamic optimization system for TRU64 Unix and Windows NT/Alpha.}
                \resumeItem{Post-link Static Optimizer Environment}{A Linux integrated performance \& analysis tool development environment.}
                \resumeItem{Hardware Adaptable Images}{Dynamic binary modification of executables based upon available hardware.}
            \resumeItemListEnd

        \resumeCompanyHeading
          {Digital Equipment Corporation}{Palo Alto, CA}
          {Senior Software Engineering Manager, Software Partner Engineering}{Jan 1994 - Jan 1998}
                \resumeItemListStart
                \resumeItem{Management}{Managed department consisting of 5 managers, 80 full-time and contract engineers, involved in supporting the migration and
                                        co-engineering of applications to OpenVMS, TRU64 Unix and Windows NT for Alpha.}
                \resumeItem{NT-Atom}{Delivered two major and several minor releases of the NT-Atom Binary Instrumentation
                             and Analysis Framework Application product.}
                \resumeItem{Database Competency Center}{Managed a team of database \& performance software engineers that worked with 
                            the major database vendors to achieve leadership TCP Benchmark results.}
                \resumeItem{Windows NT Competency Center}{Managed a team of software engineers embedded within Microsoft to support the development of applications
                            on the Windows NT for Alpha platform.}
            \resumeItemListEnd

        \resumeCompanyPositionHeading
            {Principal Software Engineer, Alpha Migration Center}{Jan 1992 - Jan 1994}
            \resumeItemListStart
            \resumeItem{Alpha Architecture}{Drove the adoption \& implementation of adding byte and word instructions operations into the Alpha Architecture.}
            \resumeItem{Fat Binaries}{Invented a method to allow for optimization and execution of applications for different generations 
                        of instruction set architectures.  Technology was shipped on Windows NT by MIcrosoft that resulted in up to 50\% application performance improvement.}
            \resumeItem{Patchwrks}{Research tool that constructed full instruction stream traces of the operating system and applications running on a processor 
                        or multiprocessor system.  Work was a continuation of a DEC System Research Center project.}
        \resumeItemListEnd
  
        \resumeCompanyPositionHeading
          {Senior Software Engineer, Government Systems Group}{Mar 1990 - Jan 1992}
          \resumeItemListStart
            \resumeItem{EPA GIS System Integration Program}{Led a 10-person team in developing all technical deliverables for the RFP, Live Test Demonstration and contract
              modifications for the successful \$140 million contract win.}
            \resumeItem{CHAMPVA}{Lead software developer for \$4.5M the Civilian Health \& Medical Program claims processing system for the 
              Department of Veterans Affairs.  Developed several device drivers, imaging scanning software and installation subsystem.  Developed in C and assember.}
            \resumeItem{NASA Space Station}{Designed the Integration, Test, Verification, Execution and Avionics Development Facility computer system for 
              RFP and subsequent award. Designed \& built prototype hardware interface for communicating with the multitude of communication busses on the simulator to
              the VAX/VMS development system.  Code was written in a mixture of ADA, FORTRAN, C and VAX assembler.}
          \resumeItemListEnd
    
        \resumeCompanyPositionHeading
          {Hardware Engineer, Laboratory Data Products}{Jun 1983 - Aug 1986}
            \resumeItemListStart
                \resumeItem{Information Transport System Decision Support System}{Prototype multimedia workstation. Developed the calendar subsystem,
                 security system (hardware and software), graphics subsystem and applications API library.  Developed in FORTRAN.}
                \resumeItem{VAXLab User Management System}{Software for automating the management of VAX/VMS systems.  Developed in DCL and BLISS-32.}
                \resumeItem{Laboratory Information Management Systems}{Developed software and API library for graphing data from various laboratory
                            instruments in real-time.  Developed in C, FORTRAN and Pascal.}
            \resumeItemListEnd
  
        \resumeCompanyHeading
          {United States Navy}{Various}
          {Naval Reserve Officer}{Sep 1985 - Dec 2016}
          \resumeJobDescription
            %{Led organizations from 25 to 1000+ personnel across multiple disciplines including surface operations, communications, 
            %computer technology, intelligence and security. Commanded 7 different units.}
            {Served on active duty from Aug 1986 to Mar 1990 \& Dec 2002 to Nov 2004}
            
    \resumeHeadingListEnd

%----- Volunteer Efforts -----
\section{\textbf{Volunteer Efforts}}
    \resumeHeadingListStart
        \resumeVolunteerHeading{Trustee, Naval War College Foundation}{2018 - present}
        \resumeVolunteerHeading{VMware Partner Advisory Board}{2019 - present}
        \resumeVolunteerHeading{Northeastern University, College of Electrical \& Computer Engineering Advisory Board}{2006 - present}
        \resumeVolunteerHeading{National University, Cyber Security and Information Assurance Advisory Council}{2010 - 2013}
        \resumeVolunteerHeading{U.S. Secretary of the Navy, National Naval Reserve Forces Policy Board}{2005 - 2008}
  \resumeHeadingListEnd
  \vspace{5pt}

%----- Patents -----
\section{\textbf{Patents}}
    \begin{tabular}{l p{475pt} l}
        \textbf{US6470493: } & Computer method and apparatus for safe instrumentation of reverse executable program modules.
    \end{tabular}

    \begin{tabular}{l p{475pt} l}
        \textbf{US6115550: } & Loader conditionally replacing a code sequence with a functionally-alike code sequence in an executable program intended for execution indifferent run-time environments.
    \end{tabular}

    \begin{tabular}{l p{475pt} l}
        \textbf{US5920721: } & Compiler generating functionally-alike code sequences in an executable program intended for execution in different run-time environments.
    \end{tabular}

  %-----------EDUCATION-----------------
\section{\textbf{Education}}
    \resumeHeadingListStart
        \resumeEducationHeading
        {Joint Staff College at National Defense University}
        {Jun 2004}
        {Diploma (Master of Arts equivalent) in Operational Planning}
        \resumeEducationHeading
        {United States Naval War College}
        {Jun 1998}
        {Diploma (Master of Arts equivalent) in Defense and Strategic Studies}
        \resumeEducationHeading
        {Northeastern University}
        {Jun 1986}
        {Bachelor of Science in Electrical and Computer Engineering}
    \resumeHeadingListEnd

%----- Program & Technical Skills -----
%\section{\textbf{Skills}}
%  \resumeHeadingListStart
%    \par
%     \textbf{Languages}{: Python, C++, SQL, Shell Scripting} \\
%      \textbf{Technologies}{: Linux, VMware, Docker, ELK, Grafana, pfSense, TrueNAS, AWS, GCE}
%  \resumeHeadingListEnd


%-------------------------------------------
\end{document}