%-------------------------
% Resume in Latex
% Author : David Hunter 
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

% ----- Select the appropriate packages below ----- 
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage[usenames,dvipsnames]{color}
\usepackage{enumitem}                     % This package provides user control over the layout of the three basic list environments: enumerate, itemize and description.
\usepackage[english]{babel}               % Change this if you want to support a different language
\usepackage{tabularx}                     % Extends the tabular to add a column to fill out the whitespace b/t two columns
\usepackage{fancyhdr}                     % For headers and footer custimization
\usepackage{lastpage}                     % Allows referring to pages in the document.  Used for x of lastpage.

% Uncomment if you need any of these optional packages.
\usepackage[hidelinks]{hyperref}          % Use if you want to have hyperlinks.
%\usepackage{latexsym}                    % Use if you need access to lasy fonts
%\usepackage{marvosym}                    % Use if you need European currency symbols.
%\usepackage{verbatim}                    % Allows printing exactly what is typed.

\input{glyphtounicode}                    % Make sure the output is parsable by resume Automatic Tracking Systems

% ----- Setup the page style options below ----- 
\fancyhf{}                                % clear all header and footer fields
\fancyfoot[C]{\thepage\ of \pageref{LastPage}}
\pagestyle{fancy}
\thispagestyle{empty}

\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-0.5in}
\addtolength{\textheight}{1.0in}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
    \vspace{-4pt}
    \scshape
    \raggedright
    \large
  }{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1                      % Ensure that generate pdf is machine readable/ATS parsable

% ----- Custom commands -----
\newcommand{\resumeEducationHeading}[3]{
  \item 
    \vspace{-5pt}
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      #1 & #2 \\
      {#3}
    \end{tabular*}
    \vspace{-20pt}
  }

  \newcommand{\resumeVolunteerHeading}[2]{
    \item 
      \vspace{-5pt}
      \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
        {#1} & #2
      \end{tabular*}
      \vspace{-30pt}
    }

% ----- Company and a single position. -----
\newcommand{\resumeCompanyHeading}[4]{
  \vspace{-1pt}
    \item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{#2} \\
      {#3} & {#4}
    \end{tabular*}\vspace{-10pt}
  }

% ----- Multiple Positions Heading in the same company -----
\newcommand{\resumeCompanyPositionHeading}[2]{
    %\vspace{-5pt}
      \item
      \begin{tabular*}{1.0\textwidth}{l@{\extracolsep{\fill}}r}
        {#1} & {#2}
    \end{tabular*}\vspace{-10pt}
}

% ----- Puts a job description under a Company -----
\newcommand{\resumeJobDescription}[1][]{
    \vspace{-1pt}\par{#1}
}

\newcommand{\resumeItem}[2]{\item{{\textbf{\small#1}}: {\small#2 \vspace{-1pt}}}}
\newcommand{\resumeSubItem}[2]{\resumeItem{#1}: {#2 \vspace{-4pt}}}
\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeHeadingListStart}{\begin{description}[leftmargin=*]}
\newcommand{\resumeHeadingListEnd}{\end{description}}

\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}}\vspace{-10pt}

% ------------------------------
%-----  Text starts below  -----
% ------------------------------
\begin{document}

%----------Heading-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
    \textbf{David Hunter} & Email : \href{mailto:dph@alumni.neu.edu}{dph@alumni.neu.edu}\\
    \href{https://linkedin.com/in/hunterdp}{https://linkedin.com/in/hunterdp} & Mobile : +1-650-814-1346
\end{tabular*}

%-----------EXPERIENCE-----------------
\section{\textbf{Experience}}
  \resumeHeadingListStart
      \resumeCompanyHeading
          {Hunter 23 Technology Services}
          {Mountain View, CA}
          {CEO}
          {Jan 2022 - present}
          \resumeJobDescription
            {A trusted advisory to start up and enterprise companies specializing in strategy development, market analysis,
            program management and technical due-dilligence in the enterprise IT market.}

      \resumeCompanyHeading
          {Hewlett Packard Enterprise}
          {San Jose, CA}
          {Vice President \& Chief Technology Officer for Strategy, Hewlett Packard Labs}
          {Mar 2015 - Nov 2021}
            \resumeItemListStart
                \resumeItem{Management}{Team of program managers and strategist to support research programs \& projects.}
                \resumeItem{Play to Win Strategy Development}{Disruptive Development, Aura Zero Trust Framework, High Performance Computing \& Trustworthy AI strategies.}
                \resumeItem{Governance Process}{Stage-gate model to manage  disruptive research projects \& existing programs.}
                \resumeItem{Information Repository}{Automated and self-service BI based system for tracking programs \& projects.}
                \resumeItem{Advisory Board}{Created an executive level business \& technical experts to advise on research activities.}
                \resumeItem{Investments \& Acquisitions}{Drove the acquisition of Simplivity, Quattro Networks and Plexxi.  Created the partnership with Platform9.}
                \resumeItem{Workloads as a Service}{Architecture that provided the ability for application workload execution brokering to the appropriate execution domain, across 
                           physical hosts, virtual machines or containers.}
                \resumeItem{HyperConverged}{Devised multiple architecture strategies to enter the HCI market, finalized by the acquisition of Simplivity.}
                \resumeItem{Technical Career Path}{Chair of two division technical promotion boards.  Member of corporate Fellow/Senior Fellow promotion board.}
            \resumeItemListEnd

      \resumeCompanyHeading
          {Hewlett Packard Enterprise}
          {San Jose, CA}
          {Vice President \& Chief Technology Officer for Strategy, Hewlett Packard Labs}
          {Mar 2015 - Nov 2021}
            \resumeItemListStart
                \resumeItem{Management}{Team of program managers and strategist to support research programs \& projects.}
                \resumeItem{Play to Win Strategy Development}{Disruptive Development, Aura Zero Trust Framework, High Performance Computing \& Trustworthy AI strategies.}
                \resumeItem{Governance Process}{Stage-gate model to manage  disruptive research projects \& existing programs.}
                \resumeItem{Information Repository}{Automated and self-service BI based system for tracking programs \& projects.}
                \resumeItem{Advisory Board}{Created an executive level business \& technical experts to advise on research activities.}
                \resumeItem{Investments \& Acquisitions}{Drove the acquisition of Simplivity, Quattro Networks and Plexxi.  Created the partnership with Platform9.}
                \resumeItem{Workloads as a Service}{Architecture that provided the ability for application workload execution brokering to the appropriate execution domain, across 
                           physical hosts, virtual machines or containers.}
                \resumeItem{HyperConverged}{Devised multiple architecture strategies to enter the HCI market, finalized by the acquisition of Simplivity.}
                \resumeItem{Technical Career Path}{Chair of two division technical promotion boards.  Member of corporate Fellow/Senior Fellow promotion board.}
            \resumeItemListEnd

        \resumeCompanyHeading
            {VMware}
            {Palo Alto, CA}
            {Chief Architect}
            {Jan 2012 - Mar 2015}
            \resumeItemListStart
                \resumeItem{Management}{30 person Platform Security Engineering \& 500 person Global Quality Engineering teams.}
                \resumeItem{Business Development}{Application of virtualization in the automotive, IoT, industrial \& entertainment markets.}
                \resumeItem{Secure Thin Hypervisor}{Bare metal hypervisor for Cloud Native Application development \& server management.}
                \resumeItem{Security Response Center}{Tools \& processes to reduce likelihood of vulnerabilities \& their impact to customers.}
                \resumeItem{CVSS for Virtualization}{Revised scoring system that better categorized vulnerabilities.}
                \resumeItem{Security Score Cards}{Engineering wide, consistent model to measure individual products against a common set of security objectives.}
                \resumeItem{Security Education/Training}{World-wide engineering formal \& informal training programs for 5,000 engineers.}
                \resumeItem{Capital Savings}{Company wide infrastructure inventory and reservation system that eliminated \$5M/year capital expense.}
                \resumeItem{Predictive Analytics}{Tools that improved testing estimations, eliminated duplicative \& identified testing gaps.}
                \resumeItem{CQE Alignment}{Realigned System \& Functional QA to development teams that improved production, increase collaboration \& decrease duplication.}
            \resumeItemListEnd
  
          \resumeCompanyPositionHeading
            {Chief Technology Officer for Worldwide Public Sector, Office of the CTO}
            {Sep 2008 - Dec 2011}
            \resumeItemListStart
                \resumeItem{Business Growth}{Evangelism contributed to growing the US Federal business from \$50M to \$500M.}
                \resumeItem{Cloud Computing}{Member of National Institute of Standards effort to develop SP-500 series.}
                \resumeItem{IPv6}{Drove the prioritized implementation of IPv6 in products to meet US Federal requirements.}
                \resumeItem{High Assurance Platform}{Moved the multi-level security domain system product from a customized hypervisor to a 
                  commercial version of VMware Workstation, including federal security assurance requirements.}
                \resumeItem{Secure Hypervisor}{Led the development of a prototype of a highly secure bare metal client hypervisor. Client platform leveraged
                  functionalities, scalability and stability of ESX while preserving device compatibility of a legacy desktop system.}
            \resumeItemListEnd
  
          \resumeCompanyPositionHeading 
          {Director of Software Engineering}
          {Nov 2004 - Sep 2008}
            \resumeItemListStart
                \resumeItem{Management}{70 person world-wide engineering organization working with OEMs and IHVs.}
                \resumeItem{Partner Support}{Created a 3-tiered OEM \& ISV support model that increased coverage of partners.}
                \resumeItem{Certification Suite}{Automated testing suite that supports over 2000 servers \& 200 storage devices.}
                \resumeItem{Hardware Compatibility List}{Transitioned from static documents to a public facing database driven website}
                \resumeItem{OEM Preferred Operating System}{New versions of vSphere supported at release by all major system OEMs.}
                \resumeItem{Security Certifications}{Achieved Common Criteria EAL 4 and FIP-140-2 cryptographic certifications.}
            \resumeItemListEnd
  
        \resumeCompanyHeading
            {SQU Systems}{Palo Alto, CA}
            {Software Consultant}{Sep 2001 - Nov 2002}
            \resumeJobDescription{
                Early stage startup working on “Software Hot Swapping” technology to patch and replace sections of a running operating
                systems.  Effort was moved off-shore and shutdown.}

        \resumeCompanyHeading
            {Home Business Magazine}{Mountain View, CA}
            {Freelance Writer \& Technical Editor} {Sep 2001 – Jul 2004}
            \resumeJobDescription {Decided to developed a book on building home networks. As technical editor wrote \& reviewed articles on technology targeted 
              towards the home business market. Magazine had a circulation of 65K newsstand copies and 22K paid subscribers.}

        \resumeCompanyHeading
            {Compaq Computer Corporation}{Palo Alto, CA}
            {Director Software Engineering, Advanced Technologies Group}{Jan 1998 - Sep 2001}
            \resumeItemListStart
                \resumeItem{Management}{20-person, multi-location engineering organization within the corporate research organization}
                \resumeItem{Digital Continuous Profiling Infrastructure}{Developed image manipulation library for Windows NT, both Intel and Alpha architectures.}
                \resumeItem{Dynamic Optimizer}{A prototype dynamic optimization system for TRU64 Unix and Windows NT/Alpha}
                \resumeItem{Post-link Static Optimizer Environment}{A Linux integrated performance \& analysis tool development environment for Linux.}
                \resumeItem{Hardware Adaptable Images}{Dynamic binary modification of executables based upon available hardware.}
            \resumeItemListEnd

        \resumeCompanyHeading
          {Digital Equipment Corporation}{Palo Alto, CA}
          {Senior Software Engineering Manager }{Jan 1990 - May 1998}
                 \resumeItemListStart
                 \resumeItem{Management}{Managed department consisting of 5 managers, 80 full-time and contract engineers, involved in supporting the migration and
                                        co-engineering of applications to OpenVMS, TRU64 Unix and Windows NT for Alpha.}
                 \resumeItem{NT-Atom}{Delivered two major and several minor releases of the NT-Atom Binary Instrumentation
                             and Analysis Framework Application product.}
                \resumeItem{Database Competency Center}{Managed a team of database \& performance software engineers that worked with 
                            the major database vendors to achieve leadership TCP Benchmark results.}
                \resumeItem{Windows NT Competency Center}{Managed a team of software engineers embedded within Microsoft to support the development of applications
                            on the Windows NT for Alpha platform.}
                \resumeItem{Patchwrks}{Research tool that constructed full instruction stream traces of the operating system and applications running on a processor 
                            or multiprocessor system.}
            \resumeItemListEnd

        \resumeCompanyPositionHeading
          {Principal Software Engineer}{Mar 1983 - Jan 1990}
          \resumeItemListStart
            \resumeItem{Alpha Architecture}{Drove the adoption and implementation of adding byte and word operations back in the Alpha Architecture.}
            \resumeItem{Fat Binaries}{Invented a method to allow for optimization and execution of applications for different generations 
              of instruction set architectures.  Implemented on Windows NT/Alpha that resulted in up to 50\% application performance improvement.}
            \resumeItem{EPA GIS System Integration Program}{Led a 10-person team in developing all technical deliverables for the RFP, Live Test Demonstration and contract
              modifications for the successful \$140 million contract win.}
            \resumeItem{CHAMPVA}{Lead software developer of the claims processing system for the Civilian Health \& Medical Program of the 
              Department of Veterans Affairs.  Developed several device drivers, imaging scanning software and installation subsystem.}
            \resumeItem{NASA Space Station}{Designed the Integration, Test, Verification and Execution and Avionics Development Facility computer system for 
              RFP and subsequent award. Built  prototype interface module for communicating with the multitude of communication busses on the simulator. 
              Code was written in a mixture of ADA, FORTRAN, C and VAX assembler.}
          \resumeItemListEnd
    
        \resumeCompanyPositionHeading
          {Hardware Engineer}{Jun 1983 - Aug 1986}
            \resumeItemListStart
                \resumeItem{Information Transport System Decision Support System}{Lead engineer that developed a prototype multimedia workstation. 
                            Developed the calendar subsystem, security system (hardware and software), graphics subsystem and applications library.}
                \resumeItem{VAXLab User Management System}{Software for automating the management of VAX/VMS systems.}
                \resumeItem{Laboratory Information Management Systems}{Developed the software and API library set for graphing 
                            data from various laboratory instruments in real-time.}
            \resumeItemListEnd
  
        \resumeCompanyHeading
          {United States Navy}{Various}
          {Naval Reserve Officer}{Sep 1985 - Dec 2016}
          \resumeJobDescription{Led organizations from 25 to 1000+ personnel across multiple disciplines including surface operations, communications, 
          computer technology, intelligence and security. Commanded 7 different units.  Served on active duty from Aug 1986 to Mar 1990, Dec 2002 to Nov 2004}
            
    \resumeHeadingListEnd

%----- Volunteer Efforts -----
\section{\textbf{Volunteer Efforts}}
    \resumeHeadingListStart
    \resumeVolunteerHeading{Trustee, Naval War College Foundation}{2018 - present}
    \resumeVolunteerHeading{VMware Partner Advisory Board}{2019 - 2022}
    \resumeVolunteerHeading{Northeastern University, College of Electrical \& Computer Engineering Advisory Board}{2006 - present}
    \resumeVolunteerHeading{National University, Cyber Security and Information Assurance Advisory Council}{2010 - 2013}
    \resumeVolunteerHeading{U.S. Secretary of the Navy, National Naval Reserve Forces Policy Board}{2005 - 2008}
  \resumeHeadingListEnd
  \vspace{5pt}
%-----------EDUCATION-----------------
\section{\textbf{Education}}
\resumeHeadingListStart
    \resumeEducationHeading
        {Joint Staff College at National Defense University}
        {Jun 2004}
        {Diploma (Master of Arts equivalent) in Strategy and Operational Planning}
        \resumeEducationHeading
        {United States Naval War College}
        {Jun 1998}
        {Diploma (Master of Arts equivalent) in National Security and Strategic Studies}
        \resumeEducationHeading
        {Northeastern University}
        {Jun 1986}
        {Bachelor of Science in Electrical and Computer Engineering}
    \resumeHeadingListEnd

%----- Patents -----
%\section{Patents \& Published Papers}
%    \resumeHeadingListStart
%        \resumeItemListStart
%            \resumeItem{111111}{...}
%            \resumeItem{22222}{...}
%            \resumeItem{333333}{}
%        \resumeItemListEnd
%\resumeHeadingListEnd


%----- Program & Technical Skills -----
%\section{\textbf{Skills}}
%  \resumeHeadingListStart
%    \par
%     \textbf{Languages}{: Python, C++, SQL, Shell Scripting} \\
%      \textbf{Technologies}{: Linux, VMware, Docker, ELK, Grafana, pfSense, TrueNAS, AWS, GCE}
%  \resumeHeadingListEnd


%-------------------------------------------
\end{document}
